---
title: "ProjectPackageInstallment3"
author: "Amina Asghar"
data: "4/27/2023"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ProjectPackageInstallment3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4,
  fig.retina = 4
)
```


```{r}
library(knitr)
library(rmarkdown)
```


```{r setup}
library(ProjectPackageInstallment3)
```

# Introduction
The package "ProjectPackageInstallment3"is simple and intuitive package that is 
created for optimizing and facilitating the process of t-tests analysis for 
given data, and then extract and visualize useful information and results.This 
package consists of three functions. These three functions include a constructor function, a print function and a plot function. More information about each of
these functions is provides as follows:

1. "myttest": This is a constructor function that that will conduct a suitable    
              t-test(T-test, Welch or paired) for the data.

2. "print.Rttest": This function will show the confidence interval for a given 
                   given confidence level. 

3. "plot.Rttest": This function will generate side by side box plots of non  
                  paired data and appropriate box plot of paired data.

This vignette will provide further detail about how these function work, and 
how to use them. 
 
## OOP
In this package we will be using `S3` OOP -- which is the commonly used object oriented form in R package making.

See <https://adv-r.hadley.nz/s3.html> for more information.

## Documentation

There should be two forms of documentation
  
  1. Function specific using Roxygen.
  2. Vignette -- long form.

# Constructor

The first function is 'myttest' function is the constructor function of this package. this function will 
take two data vectors x and y, an alpha level (significance level)  with a 
default value of 0.05, a Boolean argument "paired" which is TRUE when data is 
paired and FALSE when data in not paired and the default value of paired is set
to FALSE.   The constructor function will check whether the data is paired or
not. If the data is paired, then , we run the relevant t-test, where the 
argument paired is set to TRUE. 

If the data is not paired, then , an f-test is 
conducted to check for equality of variances.Subsequently,  appropriate t-test 
is conducted depending the variances are qual or not. After conducting the 
appropriate t-test, a list a returned that contains the following items:
1. Type of test conducted , "Welch", "T-Test" 
or "Paired" t-test was conducted
2. A Y/N (Y= Yes, N = No) conclusion to whether we reject the null hypotheis or
not at the alpha level of significance, 
3. summary statistics made by the appropriate t.test
4. The data in a list (data vectors x and y ).
This information in this list is then processed by method functions. 

## Example constructor 
```{r}
library(ProjectPackageInstallment3)
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y=rnorm(30,mean=8,sd=15)
instance_1=ProjectPackageInstallment3::myttest(x,y,alpha=0.05,paired=FALSE)

set.seed(32); x=rnorm(30,mean=10,sd=5)
set.seed(35); y=rnorm(30,mean=8,sd=15)
instance_2=ProjectPackageInstallment3::myttest(x,y,alpha=0.05,paired=FALSE)


set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y = x+ rnorm(30, 5 ,4)
instance_3=ProjectPackageInstallment3::myttest(x,y,alpha=0.05,paired=TRUE)
```

Notice that the output is of class `r class(instance_1)`

The function returns a list of components:
```{r}
names(instance_1)
```

The components can then be operated on by an appropriate method attached to a generic.

# Method


# print.Rttest Function

print.Rttest function will take an object of the class "Rttest" and print t test
results.The print function will print A(1-alpha)*100 confidence interval for
mu_x - mu_y. 
The method is attached to the generic function `print()`

```{r}
print(instance_1)
```

```{r}
print(instance_2)
```

```{r}
print(instance_3)
```


# plot.Rttest Function
The plot.Rttest function is used to plot t-test results. This function will take
an object of the class "Rttest". The function generates appropriate box plots 
for input data. 

If the data is unpaired, then, the plot.Rttest function will provide side by 
side box plots of x and y. On the other hand, if the data is paired, then,the 
function will make a box plot of differences. Furthermore, the confidence 
interval  for the difference of means is plotted inside the box plot of 
differences. The function also ensures that all the boxplots are well labelled. 

The method is attached to the generic function `plot()`
```{r}
plot(instance_1)
```

```{r}
plot(instance_2)
```

```{r}
plot(instance_3)
```


# Shiny server

These two functions(print and plot) have been placed into a shiny app and can be
invoked using the following. 

```{r,eval = FALSE}
shinyTtestAnalysis()
```
